Supplement 1

### 2020-11-05 paper/supplement-1.Rmd
edit wording.
grammar.
edit writing.

Data could be considered MCAR if an Australian Football data collector happened
to take a lunch break during the third quarter of a match, resulting in data not
being recorded for this time period. Data is MCAR, because the missings are not
systematically related to other measured variables. It would also require that this lunch break related issue didn't systematically repeat itself. That is, it is completely random.

@@

Data MNAR is when the missings are related to something unobservable or something unobserved. The previous example of data MAR could be data MNAR if the surface type was not recorded in the dataset - it would then be unobserved. Data MNAR also arises when missing values are related to the values missing. This could take place if, for example, the scales used only go up to 110Kg, and then produce missing values. This is a systematic issue - it happens each time, and means that heavier players are not recorded.

>>>>

Data could be considered MCAR if an Australian Football data collector happened
to take a lunch break during the third quarter of a match, resulting in data not
being recorded for this time period. Data is MCAR, because the missings are not
systematically related to other measured variables. For data to be MCAR, this lunch break related issue would need to occur completely at random, not systematically repeated each game.

@@

Data MNAR is when the missings are related to something unobservable or unobserved. The previous example of data MAR could be data MNAR if the surface type was not recorded in the dataset---it would then be unobserved. Data MNAR also arises when missing values are related to the values missing. This could take place if, for example, the scales used only measure up to 110 Kg, and then produce missing values. This is a systematic issue---it happens each time, and means that heavier players are not recorded.
